Spatial variation of coronal Fourier power spectra

### 2016-08-01 tex/paper2/paper2.tex
adding in placeholders for results

{\BF AIA} observes images of the Sun in multiple channels
simultaneously and continuously, at high cadence (12 seconds) and at
high spatial resolution (0.6 arcseconds per pixel).  {\BF AIA} data
was acquired using the Lockheed Martin Solar Astrophysics cutout
service at {\it http://lmsal.com/get\_aia\_data/}.  Six hours of image
data in the time range 2012-09-23 00:00 - 06:00 UT, at the full 12
second cadence, in EUV wavebands \allaiaeuv\ are used.

@@

The second stage determines which model is preferred.  Firstly, we
restrict attention to \Fpa\ that have good fits (as defined above) for
all the models considered.  Then, we use the Bayesian Information
Criterion (BIC) determine which model is substabtially preferred to
another.  The model $M_{k}$ is preferred if
\begin{equation}
\label{eqn:bic}
BIC_{k} - BIC_{j} \le -6, \forall j\ne k.
\end{equation}
This selection criterion picks the model that is substantially better
descriptions of the data compared to the other models used.  If no
model passes the selection criterion, then the \Fps\ arising from the
time-series at this pixel fails this criterion and is not retained in
the results below.  Only \Fpa\ that pass this two stage filter process
are retained for further analysis.

@@

\begin{figure}
\label{fig:spatialdistribution:preference}

\caption{Spatial distribution of model preference.}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:powerlawindex}

\caption{Spatial distribution of the power law indices.  Power law
  indices are taken from either model $M_{1}$ or $M_{2}$, whichever
  model is preferred at each pixel (see Section \ref{sec:anal})}
\end{figure}

@@

\caption{Spatial distribution of the Gaussian amplitude}
\end{figure}

@@

>>>>

{\BF AIA} observes images of the Sun in multiple channels
simultaneously and continuously, at high cadence (12 seconds) and at
high spatial resolution (0.6 arcseconds per pixel).  {\BF AIA} data
was acquired using the Lockheed Martin Solar Astrophysics cutout
service at {\it http://lmsal.com/get\_aia\_data/}.  Six hours of image
data in the time range 2012-09-23 00:00 - 06:00 UT, at the full 12
second cadence, in EUV wavebands \allaiaeuv\ are used.  
\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
}
\caption{Example images from each of the AIA channels studied.}
\label{fig:allimages}
\end{figure}

@@

The second stage determines which model is preferred.  Firstly, we
restrict attention to \Fpa\ that have good fits (as defined above) for
all the models considered.  Then, we use the Bayesian Information
Criterion (BIC) determine which model is substabtially preferred to
another.  The model $M_{k}$ is preferred if
\begin{equation}
\label{eqn:bic}
BIC_{k} - BIC_{j} \le -6, \forall j \neq k.
\end{equation}
This selection criterion picks the model that is substantially better
descriptions of the data compared to the other models used.  If no
model passes the selection criterion, then the \Fps\ arising from the
time-series at this pixel fails this criterion and is not retained in
the results below.  Only \Fpa\ that pass this two stage filter process
are retained for further analysis.

@@

\begin{figure}
\label{fig:spatialdistribution:preference}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
}
\caption{Spatial distribution of model preference.}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:powerlawindex}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
}
\caption{Spatial distribution of the power law indices.  Power law
  indices are taken from either model $M_{1}$ or $M_{2}$, whichever
  model is preferred at each pixel (see Section \ref{sec:anal})}
\end{figure}

@@

\caption{Spatial distribution of the ratio $\max[P_{1}(\nu)/G(\nu)]$.}
\end{figure}

\caption{Spatial distribution of $\arg\max[P_{1}(\nu)/G(\nu)]$.}
\end{figure}

@@

PSF removal

De noising algorithms
